Learning and comparing functional connectomes across subjects

### 2012-12-30 paper.tex
minor edits

\paragraph{Regions from atlases}
%
Atlases can be used to define full-brain parcellations. The most popular
choice is probably the AAL atlas \cite{tzourio-mazoyer2002a}, that
benefits from an SPM toolbox. However, it suffers from major
shortcomings; namely that \emph{i)} it was defined on a single subject
and thus does does not reflect inter-subject variability and \emph{ii)}
focuses on labeling large anatomical structures and does not match
functional layout --for instance only two regions describe the medial
part of the frontal lobe. Multi-subject probabilistic altases such as the
Harvard-Oxford atlas distributed with FSL \cite{smith2004} or the
sulci-based structural atlas used in \cite{varoquaux2010c} mitigate the
first problem, and the high number of regions defined using sulci also
somewhat circumvent the second problem (see
fig.\,\ref{fig:parcellations}).

@@

\paragraph{FMRI-based function definition}
%
Defining regions directly from the fMRI signal brings many benefits.
First, it can capture subject-specific functional information. Second, it
also adapts to the signal at hand and it's limitations, such as
EPI-specific warps or vascular and movement artifacts that are isolated
in ICA-like approaches. The simplest approach to define task-specific
regions is to use activation maps derived from standard GLM-based
analysis in a task-driven study (see for instance \cite{poldrack2011}).
Regions are extracted by thresholding the maps, or using balls around the
activation peaks. For resting-state studies, unsupervised multivariate
analysis techniques are necessary. Clustering approaches extract
full-brain parcellations \cite{craddock2011, bellec2010, yeo2011,
thirion2006}, and have been shown to extract well-known functional
structures from rest data \cite{yeo2011}. Alternatively, decompositions
methods, such as ICA \cite{beckmann2004}, can unmixing linear
combinations of multiple effects and separate out multiple spatial maps
capturing functional networks or confounding effects. At high model
order, ICA maps define a functional parcellation \cite{kiviniemi2009}.
Extracting regions from these maps requires additional effort as they can
display fragmented spatial features and structured background noise, but
incorporating sparsity and spatial constraints in the decomposition
techniques leads to contrasted maps that outline many different
structures \cite{varoquaux2012} (see fig.\,\ref{fig:parcellations}).

>>>>

\paragraph{Regions from atlases}
%
Atlases can be used to define full-brain parcellations. The most popular
choice is probably the AAL atlas \cite{tzourio-mazoyer2002a}, that
benefits from an SPM toolbox. However, it suffers from major
shortcomings; namely \emph{i)} that it was defined on a single subject
and thus does does not reflect inter-subject variability and \emph{ii)}
that it focuses on labeling large anatomical structures and does not match
functional layout --for instance only two regions describe the medial
part of the frontal lobe. Multi-subject probabilistic altases such as the
Harvard-Oxford atlas distributed with FSL \cite{smith2004} or the
sulci-based structural atlas used in \cite{varoquaux2010c} mitigate the
first problem, and the high number of regions defined using sulci also
somewhat circumvent the second problem (see
fig.\,\ref{fig:parcellations}).

@@

\paragraph{FMRI-based function definition}
%
Defining regions directly from the fMRI signal brings many benefits.
First, it can capture subject-specific functional information. Second, it
adapts to the signal at hand and its limitations, such as
EPI-specific warps or vascular and movement artifacts that are isolated
in ICA-like approaches. The simplest approach to define task-specific
regions is to use activation maps derived from standard GLM-based
analysis in a task-driven study (see for instance \cite{poldrack2011}).
Regions are extracted by thresholding the maps, or using balls around the
activation peaks. For resting-state studies, unsupervised multivariate
analysis techniques are necessary. Clustering approaches extract
full-brain parcellations \cite{craddock2011, bellec2010, yeo2011,
thirion2006}, and have been shown to extract well-known functional
structures from rest data \cite{yeo2011}. Alternatively, decompositions
methods, such as ICA \cite{beckmann2004}, can unmixing linear
combinations of multiple effects and separate out multiple spatial maps
capturing functional networks or confounding effects. At high model
order, ICA maps define a functional parcellation \cite{kiviniemi2009}.
Extracting regions from these maps requires additional effort as they can
display fragmented spatial features and structured background noise, but
incorporating sparsity and spatial constraints in the decomposition
techniques leads to contrasted maps that outline many different
structures \cite{varoquaux2012} (see fig.\,\ref{fig:parcellations}).
